Job mobility and earnings growth: diffrerent markets, different outcomes.

### 2018-09-07 draft.Rmd
Update draft.Rmd

Institutional differences in rewarding mobility rarely appear in theoretical literature. In the *job-matching* model mobility stems from a mismatch between a worker's skills, and her rewards or conditions (Jovanvich). In this way countries with low rates of job mobility, are simply countries with a good record of job matching. In the *job-search* model mobility stems from the opportunity of higher wages. Thus if labour markets have a wide dispersion of wages workers have more opportunity to match their reservation wages, which leads to more mobility. *Human capital* theorists would see mobile labour markets as those with a high dependence on transferable skills, and less mobile countries as those dependent on firm- specific skills.

>>>>

Institutional differences in rewarding mobility rarely appear in theoretical literature. In the *job-match* model mobility stems from a mismatch between a worker's skills, and her rewards or conditions (Jovanvich). In this way countries with low rates of job mobility, are simply countries with a good record of job matching. In the *job-search* model mobility stems from the opportunity of higher wages. Thus if labour markets have a wide dispersion of wages, workers have more opportunity to match their reservation wages, which leads to more mobility. In *Human capital* theory, job mobility depends on the type of skills available to workers, either tranferable or firm specific. Thus, mobile labour markets have a high dependence on transferable skills between firms, while less mobile markets exist among firms that rely on on firm-specific skills.

Studies exploring mobility rarely consider the impact local institutions make on the observed labour market. Typically, authors use data for a given labour market and estimate the effects of quits on earnings growth for individuals or groups. Rarely do authors compare and contrast the impact of quits in two separate markets. Beyond this, authors often ignore the impact of internal promotions on earnings growth. Quits are a form of mobility, but so are promotions who have an impact on wages.
